A Study of Immersion Factors Using an Augmented Reality Simulation

### 2009-06-25 Paper/paper.tex
Added subsection for participants

>>>>

\subsection(Participants)

We ran this experiment on 19 subjects, 11 were male, and 8 female.  The participants ranged in age from 23 to 59, 15 were in the range 23 to 30, and the remaining 4 in the range 51 to 49.  None were colorblind.  Most users were heavy computer users with at least somewhat familiarity with virtual reality and augmented reality.  Only one participant played 3D video games often.  After every 9 trials we had the participants take a mandatory 5 minute break.  Some experienced light fatigue, but none experienced any strong effects of motion sickness.
